comgen-outline

### 2017-08-29 paper/comgen-paper.Rmd
edits up to model simulation section

<!-- We propose that generic language and other forms of genericity information convey information about probabilities that underly generalization and prediction. -->
<!-- We posit that the conceptual factors of the kind discussed by Prasada, Leslie, and colleagues influence the meaning of a generic statement via their influence on probabilities.  -->
<!-- Bayesian cognitive models have been shown to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodmanconcepts]. -->
<!-- The basic currency of inductive reasoning in these models is probability. -->
<!-- If generalizations in language convey information about probabilties, then a relatively simple semantic theory (e.g., a threshold on probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$: -->

<!-- We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section.  -->

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008; cf., $Prasada2006; Prasada2013].
We term this prior distribution the **prevalence prior**.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.

>>>>

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according the meaning of an utterance $u$.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
This component of the model provides a potential bridge to conceptual account of generics [e.g., @Leslie2007; Prasada2006; Prasada2013].
Critically in our model, this structure is in listener's knowledge of the world $P(h)$ and not in the semantic content of the utterance $u$. 
<!-- Our proposal that generic language and other forms of communicating generalizations convey information about probabilities that underly generalization and prediction implies that the conceptual factors of the kind discussed by Prasada, Leslie, et al. influence the meaning of a generic statement via their influence on subjective probability. -->
<!-- Flexible, structured models of the world have been shown to do just that in the case of generalizations from observations, merging structured representations with probabilisitic inference [e.g., @Kemp2008; @Goodmanconcepts]. -->
We term this prior distribution the **prevalence prior**.
